---
title: "First R Markdown Post"
author: "Frida Gomam"
date: 2022-01-09T21:13:14-05:00
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

## first one

a) Every number in $[0, 1]$ has a ternary expansion

$x=\sum_{k=1}^{\infty}\frac{a_k}{3^k},$ where ${a_k}=0,1,2$

Prove that  $x\in\mathcal{C}$, the Cantor set, if and only if x has a representation as above where every ak is either $0$ or $2$.

Proof. (⇒) Let $x\in\mathcal{C}.$  We build a ternary expansion for x of the desired form as follows.Consider C1. It must
be that x belongs to one of $[0,\frac{1}{3}]$ (in which case let first digit of the ternary expansion for $x$ be $0$) or $[ \frac{2}{3},1]$ (in
which case let first digit of the ternary expansion for $x$ be $2$). Next, consider C2. The interval of C1 to which
x currently belongs will be divided into three subintervals, and so we append a 0 to the ternary expansion
of x if it belongs to the leftmost subinterval or a 2 if it belongs to the rightmost subinterval. Continuing in
this way, we see that x has an associated ternary expansion containing only the digits 0 and 2.

(⇐) Let$x=\sum_{k=1}^{\infty}\frac{a_k}{3^k},$ where ${a_k}=0,1,2$

We can locate x on the real line as follows. If a1 = 0, we choose the left subinterval of C1. If a1 = 2,
we choose the rightmost subinterval of C1. When we form C2, the interval we have just chosen will be
subdivided into three subintervals. If a2 = 0, we select the leftmost subinterval. If a2 = 2, we select the
rightmost subinterval. Continue in this way. Since the length of these intervals can be made arbitrarily
small, we see that the ternary expansion of x uniquely specifies its location on the real line.

```{r echo=FALSE}
blogdown::shortcode('tweet', '450533554011656192')
```



