---
title: "Python I"
author: ''
date: "2022-12-23"
output:
  html_document:
    df_print: paged
categories: []
tags: []
slug: "python-i"
---

## Scrape data from web 

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- library(reticulate) -->
<!-- py_install("bs4") -->
<!-- py_install("requests") -->
<!-- conda_remove() -->
<!-- ``` -->

```{python}
#IMPORT LIBRARIES
from bs4 import BeautifulSoup
import requests
#IMPORT CSV LIBRARY
import csv
#OPEN A NEW CSV FILE. IT CAN BE CALLED ANYTHING
file= open('ecommerce.csv', 'w')
#CREATE A VARIABLE FOR WRITING TO THE CSV
writer = csv.writer(file)
#CREATE THE HEADER ROW OF THE CSV
writer.writerow(['Date', 'Content'])
#REQUEST WEBPAGE AND STORE IT AS A VARIABLE
page_to_scrape = requests.get("https://internetcommerce.netlify.app/")
print(page_to_scrape)
#USE BEAUTIFULSOUP TO PARSE THE HTML AND STORE IT AS A VARIABLE
soup = BeautifulSoup(page_to_scrape.text, 'html.parser')
#FIND ALL THE ITEMS IN THE PAGE WITH A CLASS ATTRIBUTE OF 'TEXT'
#AND STORE THE LIST AS A VARIABLE
quotes = soup.findAll('a', attrs={'class':'archive-item-link'})
#FIND ALL THE ITEMS IN THE PAGE WITH A CLASS ATTRIBUTE OF 'AUTHOR'
#AND STORE THE LIST AS A VARIABLE
authors = soup.findAll('span', attrs={'class':'archive-item-date'})

#LOOP THROUGH BOTH LISTS USING THE 'ZIP' FUNCTION
#AND PRINT AND FORMAT THE RESULTS
for date, content in zip(authors, quotes):
    print(date.text.strip()+ "(" + content.text.strip() + ")")
    #WRITE EACH ITEM AS A NEW ROW IN THE CSV
    writer.writerow([date.text.strip(), content.text.strip()])
#CLOSE THE CSV FILE
file.close()
```

- I learned the code from the [YouTube](https://www.youtube.com/watch?v=RvCBzhhydNk) 

- But the date column in the csv file does not show up, I got help from [StackExchange](https://stackoverflow.com/questions/74893872/how-to-show-dates-in-csv-file-generated-by-python)

## How to make table?

- I have to use `tabulate` to make table, the code does not work in my `RStudio` since the package is not installed. I learn to install the package from [here](https://rstudio.github.io/reticulate/articles/python_packages.html):


```{r include=FALSE}
library(reticulate)
py_install("tabulate")
```

- I copied the example from [here](https://rstudio.github.io/reticulate/articles/r_markdown.html):

```{r eval=FALSE, include=FALSE}
library(reticulate)
py_install("matplotlib")
```



```{python}
import matplotlib.pyplot as plt 
import numpy as np
t=np.arange(0.0, 2.0, 0.01)
s=1+np.sin(2*np.pi*t) 
plt.plot(t,s)
plt.xlabel('time(s)')
plt.ylabel('voltage(mv)') 
plt.grid(True)
plt.savefig("test.png")
plt.show()
```

- print the scraped data into a table from [here](https://www.statology.org/create-table-in-python/):

```{r include=FALSE}
library(reticulate)
py_install("tabulate")
py_install("pandas")

# conda installation causes a lot of problems!
# create a new environment 
#conda_create("r-reticulate")

# install tabulate
#conda_install("r-reticulate", "tabulate")

# import tabulate (it will be automatically discovered in "r-reticulate")
# tabulate <- import("tabulate")
```


```{python}
import pandas
from tabulate import tabulate
data=pandas.read_csv("ecommerce.csv")
print(tabulate(data,headers=data.head(), tablefmt="grid", showindex="always"))
```

